---
title: <font size="5"> Report of linkage disequilibrium </font> 
output: html_document
---

<style>
  .col2 {
    columns: 2 200px;         
    -webkit-columns: 2 200px; 
    -moz-columns: 2 200px;    
  }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(shiny)
library(rmarkdown)
library(kableExtra)
library(knitr)
```

<div class="col2">

**Table 1**: Number of individual genotypes

```{r, echo=FALSE}
dt <- kable(LD()[[1]])
kable_styling(dt, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

**Table 2**: The expected frequency of haplotypes + alleles frequency

```{r, echo=FALSE}
dt2 <- kable(LD()[[2]])
kable_styling(dt2, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

</div>

**Table 3**: The expected and observed frequency (and the number) of haplotypes

```{r, echo=FALSE}
dt3 <- kable(LD()[[3]])
kable_styling(dt3, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

**Table 4**: The expected frequency of haplotypes in terms of linkage disequilibrium + alleles frequency

```{r, echo=FALSE}
dt4 <- kable(LD()[[4]])
kable_styling(dt4, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

**Table 5**: Basic statistics of linkage disequilibrium

```{r, echo=FALSE}
dt5 <- kable(LD()[[5]])
kable_styling(dt5, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

<div class="col2">
**Table 6**: Combined (observed) number of genotypes

```{r, echo=FALSE}
dt6 <- kable(LD()[[6]])
kable_styling(dt6, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

**Table 7**: Combined (expected) number of genotypes

```{r, echo=FALSE}
dt7 <- kable(LD()[[7]])
kable_styling(dt7, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

</div>

**Table 8**: Chi - square test for linkage disequilibrium between two loci

```{r, echo=FALSE}
dt8 <- kable(LD()[[8]])
kable_styling(dt8, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```
